---
title: "Assignment 3"
author: "Megha"
date: "11/9/2021"
output: pdf_document
---
## Introduction
For this assignment, I will be looking at Hospital data to plot the 30 day
mortality rates for heart attack, finding the best hospital in the state, 
ranking hospitals by outcome in a state, and finally ranking hospitals in all 
states. 

Source: The data from this assignment comes from the [Hospital Compare web site](https://www.cms.gov/Medicare/Quality-Initiatives-Patient-Assessment-Instruments/HospitalQualityInits/HospitalCompare). This website provides data and
information about the quality of care at over 4,000 Medicare-certified hospitals
in the U.S. This dataset essentially covers all major U.S. hospitals.

The files I will be using from this dataset are:

* **outcome-of-care-measures.csv**: Contains information about 30-day mortality and readmission rates
for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.
* **hospital-data.csv**: Contains information about each hospital.

## Working with the Data

```{r}
## reading data into R
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
hosp <- read.csv("hospital-data.csv", colClasses = "character")

## looking at the data
head(outcome)
head(hosp)
names(outcome) ## to determine column names

## Plotting the 30 - day mortality rates for heart attack - from column 11
outcome[, 11] <- as.numeric(outcome[, 11])
hist(outcome[, 11],xlab = "Days", ylab = "Mortality Rate", main = "30 Day Mortality Rates for Heart Attack")
```
Next, I'm going to find the best hospital in a state by writing a function that takes two arguments and returns the best (or lowest)30-day mortality for the specified outcome.
```{r}
source("best.R")
## Sample Outputs:
best("TX", "heart attack")
best("TX", "heart failure")
best("MD", "heart attack")
best("MD", "pneumonia")
best("PR","pneumonia")
```
Next, I will write a function that returns the name of the hospital in a specified state based on a ranking system for a given outcome. 

```{r}
source("rankhospital.R")
#Sample outputs
rankhospital("TX", "heart failure", 4)
rankhospital("MD", "heart attack", "worst")
rankhospital("MN", "heart attack", 5000)
```
Finally, I will write a function that returns the name of a hospital from each state based on a specified rank and outcome. 
```{r}
source("rankall.R") 
head(rankall("heart attack", 20), 10)
tail(rankall("pneumonia", "worst"), 3)
tail(rankall("heart failure"), 10)
```

